\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2013-01-15 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
new 'pattern' argument to filterNA
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@71957 bc3139a8-67e5-0310-9ffc-ced21a209358
knity 1.0 compatibility
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@72561 bc3139a8-67e5-0310-9ffc-ced21a209358

%\VignetteIndexEntry{Base Functions and Classes for MS-based Proteomics}
%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Infrastructure, Bioinformatics, quantitative }
%\VignettePackage{MSnbase-demo}
\documentclass{article}
\usepackage[nogin]{Sweave}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

<<quantify, echo=TRUE, cache=FALSE, keep.source=TRUE>>=
qnt <- quantify(experiment,
                method = "trap",
                reporters = iTRAQ4,
                strict = FALSE,
                parallel = FALSE,
                verbose = FALSE)
qnt
head(exprs(qnt))
@

@@

@@

<<incompdiss, echo=TRUE, cache=FALSE, keep.source=TRUE>>=
iTRAQ5
incompdiss <- quantify(itraqdata,
                       method = "trap",
                       reporters = iTRAQ5,
                       strict = FALSE,
                       parallel = FALSE,
                       verbose = FALSE)
head(exprs(incompdiss))
@

@@

\section{Session information}\label{sec:sessionInfo} 
<<label='sessioninfo', results=tex, echo=FALSE, cache=FALSE>>=
toLatex(sessionInfo())
@

>>>>

%\VignetteIndexEntry{Base Functions and Classes for MS-based Proteomics}
%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Infrastructure, Bioinformatics, quantitative }
%\VignettePackage{MSnbase-demo}
\documentclass{article}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

<<quantify, echo=TRUE, cache=FALSE, tidy=FALSE>>=
qnt <- quantify(experiment,
                method = "trap",
                reporters = iTRAQ4,
                strict = FALSE,
                parallel = FALSE,
                verbose = FALSE)
qnt
head(exprs(qnt))
@

@@

The filtering criteria for \Rfunction{filterNA} can also be defined as a pattern
of columns that can have missing values and columns that must not exhibit any. 
See \Rfunction{?filterNA} for details and examples.

@@

<<incompdiss, echo=TRUE, cache=FALSE, tidy=FALSE>>=
iTRAQ5
incompdiss <- quantify(itraqdata,
                       method = "trap",
                       reporters = iTRAQ5,
                       strict = FALSE,
                       parallel = FALSE,
                       verbose = FALSE)
head(exprs(incompdiss))
@

@@

\section{Session information}\label{sec:sessionInfo} 
<<sessioninfo, results='asis', echo=FALSE, cache=FALSE>>=
toLatex(sessionInfo())
@
